---
title: "iPhone or iGo (to the Gym)"
author: "Griffin Barich"
date: "12/10/19"
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "~/Documents/Documents - Griffin’s MacBook Pro/Senior Year/Fall_2019/Experimental Design/iGotoTheGym/Reports") })
output:
  ioslides_presentation: 
    logo: Logo.png
    css: css.css
    transition: faster
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE, warning = F, message=F)
source("~/Documents/Documents - Griffin’s MacBook Pro/Senior Year/Fall_2019/Experimental Design/iGotoTheGym/Code:Data/00_Assignment_of_Experiment.R")
source("~/Documents/Documents - Griffin’s MacBook Pro/Senior Year/Fall_2019/Experimental Design/iGotoTheGym/Code:Data/03_Visualizations.R")
```

## Project Decription

This project focuses on the impact of exercise on smartphone use. This project was movitated by:

- Lots of Smartphone Use

- Available data

- Desire to go to the gym


## Research Question

__Will going to the gym affect the amount of times I pickup my phone in a day?__



## Measures {.build}

### Response Variable

>- Apple defined

>- Recorded around same time every day

### Treatment Variable

>- Went to Freeman for 30-60 minutes

>- Assigned at the beginning of the experiment (`randomizr` package)

>- Time of Day and length at gym recorded using calendar event.

## Measures (cont.) {.build}

### Blocking

>- Day types
>- Randomized with Blocking using `randomizr`.

```{r blocking_table, echo=F}
kable(blocking_tab)
```

## Data Description {.smaller}

- 42 Observations (2 missing), 5 Variables

- Day Type and Time of Day Recorded

```{r}
pickup_hist +
  geom_histogram(fill="firebrick", bins=10)+
  ggtitle("Histogram of Pickups")
```

## Data Description

```{r}
pickup_hist +
  geom_histogram(fill="firebrick", bins=10)+
  facet_grid(.~ex)+
  ggtitle("Pickups by Treatment Days")
```

## Data Description

```{r}
interaction_plot
```


## Results {.codefont}
```{r}
summary(lm_block)
```

## Checking Assumptions

```{r,fig.show='hold', echo=F}
plot(lm_block, 1)
```

## Checking Assumptions
```{r,fig.show='hold'}
plot(lm_block, 2)
```

## Serial Correlation
```{r}
ser_cor
```

## Results with Serial Correlation {.codefont}
```{r}
summary(lm_block_2)
```
<div class="notes">
Total of 10 times fewer due to dates
</div>
## Results with Length {.codefont}
```{r}
summary(lm_length)
```

## Results
```{r}
reg
```


## Discussion {.build}

>- Lasting Effects?

>- Variance of Lengths (Interpolation?)

>- Time of Day

## Validity {.build}

### Internal

>- Representative Time?

>- Travelling

### External

>- Sample Size of One

## Conclusions

There was a significant effect on pickups as a result of going to the gym. While there are issues with the experiment, we do see a causal relationship.

# Thank You

