---
title: "Project Proposal"
author: "Griffin Barich"
date: "11/01/2019"
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "Reports") })
output:
  html_document:
    df_print: paged
    code_folding: "show"
---

### Introduction Section: 

For QAC 307, I decided to focus on the impact of exercise on smartphone use in myself. I realized that I am constantly on my phone and use it whenever I am bored or nervous. I also independently took on the hypothesis that exercise will reduce general boredness/nervousness. Through the synthesis of these two concepts, I came up with this experiment. I knew that the amount of free time I had in a day would be an important factor, so I split the weekdays into 3 groups: Monday/Wednesday, Tuesday/Thursday, and the Weekend. This became my blocking variable. 

### Methods section: 
##### 1. Type of Study: 
Experimental 

##### 2. Units:

Treatments assigned using the using the method below:
```{r, echo=F, message=F}
source("Final Project/Assignment of Experiment.R")
library(dplyr)
library(randomizr)
```

1: Get Dates and Days of Week
```{r,eval=F}
dates <- seq(as.Date("2019-10-10"), as.Date("2019-11-25"), 1)
weekdays <- weekdays(dates)
df <- data.frame(dates, weekdays)
```

2: Sort Weekdays into Blocks
```{r,eval=F}
df$DayType <- ifelse(df$weekdays %in% c("Monday", "Wednesday"), "MW",
  ifelse(df$weekdays %in% c("Tuesday", "Thursday"), "TT",
  "FSS"))
```

3: Remove Fall Break and Drop Weekdays
```{r,eval=F}
"%!in%" <- function(x, y) !("%in%"(x, y))

df <- df %>%
  filter(dates %!in% seq(as.Date("2019-10-17"), as.Date("2019-10-21"), 1)) %>%
  select(-weekdays)
```

Use `randomizr` package to randomize with blocking (setting a seed)
```{r,eval=F}
set.seed(1234)
Z <- block_ra(blocks = df$DayType)

df$ex <- Z
df$ex[df$dates == "2019-11-15"] <- 1
df$ex[df$dates == "2019-11-16"] <- 0
```

Note that I did switch two dates due to a previous commitment. We still see that the distribution of treatment over the levels is even (since there are more days in the "FSS" group, there are more instances of exercise).
```{r, echo=F}
knitr::kable(table(factor(df$ex, labels=c("Exercise", "Rest")), df$DayType))
knitr::kable(table(factor(df$ex, labels=c("Exercise", "Rest")), weekdays.Date(df$dates)))
```

From the table above, we see that the distribution of exercise by weekday is not equal so it will not be a great blocking variable.


##### 3. Conditions: Describe the treatment conditions.

Treatment is me going to the gym for at least 25 minutes and being "active" while there, whatever that means to me on that day. I will admit this is a less robust portion of the experiment, but since I am recording how long I spend at the gym each time (using my calendar), it will be evident if this is a confounding variable in my final analysis.

##### 4. Response Variables: provide definitions, methods of measurement, and how you will guarantee reliability of your measurements.

My response variable is the number of times I pickup my phone in a day. Apple's Screen Time feature measures this for me. Apple's website describes it as "how many times you picked up your iPhone", and nothing more. [Link](https://support.apple.com/en-us/HT210387).

##### 5. Statistical analysis: Name the design you will use. Describe the factor structure of the data.

Randomized Design with Blocks, I will use ANOVA and regression to show if there is a relationship between pickups and exercise controlling for day of week. I will possibly also add in data about duration at the gym and time going to the gym.

##### 6. Data Collection From:

I made a calendar event each day where I record the number of pickupsm collecting between 11:30 PM and 11:59 PM. Gym times were assigned at the beginning of the experiment and have been updated to reflect my actual time at the gym.